A thermodynamic view of dusty protoplanetary disks

### 2017-07-12 paper.tex
added reference to latter 17 and squires 17 in intro, need to add later hopkins 17

%\title{On the entropy of 
%  isothermal dusty gas: application to protoplanetary disks}  
\title{A thermodynamic view of dusty protoplanetary disks}
 % \title{Dust-free modeling of dusty protoplanetary disks I:
%axisymmetric stability}
\author{Min-Kai Lin\altaffilmark{1,2,3}}
\author{Andrew N. Youdin\altaffilmark{2}}
%\affil{Department of Astronomy and Steward Observatory, 
%University of
 % Arizona, Tucson, AZ 85721, USA\\
%Institute of Astronomy and Astrophysics, Academia Sinica, 
%Taipei 10617, Taiwan}
\altaffiltext{1}{Institute of Astronomy and Astrophysics, Academia Sinica, 
Taipei 10617, Taiwan
}
\altaffiltext{2}{Department of Astronomy and Steward Observatory, 
University of
Arizona, Tucson, AZ 85721, USA}
\altaffiltext{3}{Steward Theory Fellow}
\email{mklin@asiaa.sinica.edu.tw}

@@

\section{Introduction}
%si, sgi as examples
Protoplanetary disks are comprised of a mixture of gas and dust
\citep{chiang10}. Although the overall dust content is small
($\sim 1\%$ by mass), their presence can have profound impacts on the 
gas dynamics and vice versa. Dust-gas friction introduces phenomena
that are absent in pure gas disks. Important examples include the
streaming instability 
\citep[SI,][]{youdin05a,youdin07b,johansen07}, secular gravitational
instabilities \citep[SGI,][]{ward00,youdin11,michikoshi12,takahashi14} and
Kelvin-Helmholtz instabilities
\citep{goldreich1973, chiang08,barranco09,lee10}. These instabilities 
can trigger turbulence, and (in different regimes) promote or inhibit 
planetesimal formation. 
More recently, new 
dusty instabilities have appeared in numerical
simulations \citep{loren15,loren16,lamb16}, but their physical underpinnings are not yet well
understood.

>>>>

%\title{On the entropy of 
%  isothermal dusty gas: application to protoplanetary disks}  
\title{A thermodynamic view of dusty protoplanetary disks}
 % \title{Dust-free modeling of dusty protoplanetary disks I:
%axisymmetric stability}
\author{Min-Kai Lin\altaffilmark{1,2,3}}
\author{Andrew N. Youdin\altaffilmark{2}}
%\affil{Department of Astronomy and Steward Observatory, 
%University of
 % Arizona, Tucson, AZ 85721, USA\\
%Institute of Astronomy and Astrophysics, Academia Sinica, 
%Taipei 10617, Taiwan}
\altaffiltext{1}{Institute of Astronomy and Astrophysics, Academia Sinica, Taipei 10617, Taiwan}
\altaffiltext{2}{Department of Astronomy and Steward Observatory, University of Arizona, Tucson, AZ 85721, USA}
\altaffiltext{3}{Steward Theory Fellow}

\email{mklin@asiaa.sinica.edu.tw}

@@

\section{Introduction}
%si, sgi as examples
Protoplanetary disks are comprised of a mixture of gas and dust
\citep{chiang10}. Although the overall dust content is small
($\sim 1\%$ by mass), their presence can have profound impacts on the 
gas dynamics and vice versa. Dust-gas friction introduces phenomena
that are absent in pure gas disks. Important examples include the
streaming instability 
\citep[SI,][]{youdin05a,youdin07b,johansen07}, secular gravitational
instabilities \citep[SGI,][]{ward00,youdin11,michikoshi12,takahashi14,latter17} and 
Kelvin-Helmholtz instabilities
\citep{goldreich1973, chiang08,barranco09,lee10}.

These instabilities can trigger turbulence, and (in different regimes) promote or inhibit  
planetesimal formation. 
More recently, new 
dusty instabilities have appeared in numerical  
simulations \citep{loren15,loren16,lamb16} and analytical calculations \citep{squire17},   
but their physical underpinnings are not yet well 
understood.
